Algomusicology, ????, Profit

### 2016-05-29 paper.tex
Tweak.

This paper will argue that it can. It will do so by reviewing existing art works that are algorithmic in nature, and
also by using algomusicological concepts to create a new work that challenges our present conception of musical authorship and
copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays and musicology
papers.

@@

Describing the notes of a musical work as code is straightforward, as notes can be represented by simple data structures like
sequences of time/pitch tuples. Selecting which encoding scheme to use is less straightforward, because the choice of primitives
can affect the complexity score. Ultimately, the choice of music theory library is difficult, somewhat subjective and
will not be answered here.

@@

Through his Library of Babel, Borges is playing with our notions of invention versus discovery. Mathematicians and computer
scientists struggle with whether they are the inventors of new theories or discoverers. Philip Wadler, for example,
argues that the lambda calculus is such a fundamental concept that it deserves to be considered a universal concept that
was discovered\cite{Propositions as Types}. By positing a library where any work may be found if you know where to look, Borges
suggests that even literary authorship could be considered a search problem and therefore a matter of discovery rather than
creation.

>>>>

This paper will argue that it can. It will do so by reviewing existing literary and musical works that are informed by algorithmic
thinking, and also by using algomusicological concepts to create a new work that challenges our present conception of musical
authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays
and musicology papers.

@@

Describing the notes of a musical work as code is straightforward, as notes can be represented by simple data structures like
sequences of time/pitch tuples. Selecting which encoding scheme to use is less straightforward, because the choice of primitives
can affect the complexity score. Ultimately, the choice of music theory language is difficult, somewhat subjective and
has trade-offs. I will not attempt to address this choice here as it doesn't materially impact my arguments.

@@

Through his Library of Babel, Borges is playing with our notions of invention versus discovery. Mathematicians and computer
scientists struggle with whether they are the inventors of new theories or discoverers. Philip Wadler, for example,
argues that the lambda calculus is so fundamental that it deserves to be considered a universal concept that
was discovered\cite{Propositions as Types}. By positing a library where any work may be found if you know where to look, Borges
suggests that even literary authorship could be considered a search problem and therefore a matter of discovery rather than
creation.
